\documentclass[10pt,twoside,a4]{scrartcl}%

\usepackage{fontspec}%
\setmainfont{DIN Pro}%
\newfontfamily\DinProLight[Ligatures=TeX]{DIN Pro Light}%

\usepackage{polyglossia}%
%\setdefaultlanguage{dutch}%

\DeclareOldFontCommand{\sc}{\normalfont\scshape}{\@nomath\sc}%

\setkomafont{disposition}{\DinProLight}%

\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

\usepackage[unicode,
            pdfauthor={Dylan Meysmans},
            pdftitle={Testing the Land Register},
            pdfsubject={},
            pdfkeywords={},
            pdfproducer={},
            pdfcreator={}]{hyperref}%

\begin{document}%

\title{Testing the Land Register}%
\author{Dylan Meysmans}%
\date{\today}%
\maketitle%

To test the land register smart contract \texttt{Register.sol}, please use \href{https://remix.ethereum.org/#optimize=true&version=soljson-v0.5.3+commit.10d17f24.js}{the Remix IDE}\footnote{The URI we provide here already sets the proper compiler version and turns on optimization.}.
First add \texttt{Register.sol} to Remix, then perform the following steps to test it out:

\begin{enumerate}
    \item Compilation
    \begin{enumerate}
        \item On the tab marked \textbf{Compile} on the right-hand side, set the current version to \textbf{0.5.3+commit.10d17f24}, if it is not already set.
        \item On the same tab, check the box for \textbf{Auto compile} and optionally for \textbf{Enable Optimization}. 
    \end{enumerate}
    \item Execution
    \begin{enumerate}
        \item On the tab marked \textbf{Run} on the right-hand side, set the \textbf{Environment} to \textbf{JavaScript VM}.
        \item On the same tab, select the \textbf{Register} contract and click \textbf{Deploy}. This should cause an instance of the contract to pop up on the bottom of the tab.
    \end{enumerate}
    \item Registering a land
    \begin{enumerate}
        \item Still on the \textbf{Run} tab, expand the \textbf{createLand} section for the contract instance.
        \item Provide an array of x coordinates (e.g. \texttt{[0, 0, 1, 1]}) and an array of y coordinates (e.g. \texttt{[0, 1, 0, 1]}) marking the borders, the size of the land (e.g. \texttt{1}), and its value (e.g. \texttt{[0, 0, 1, 1]}).
        \item For the owner parameter, provide one of the addresses from the \textbf{Account} list on top of the \textbf{Run} tab which you did not use to deploy the contract.
        \item Click the \textbf{transact} button.
        \item Expand the output of the \texttt{createLand} transaction on the console on the bottom of the window and read the \textbf{decoded output} field in the table to find out the unique code of the land registered. It is necessary to sell the land in the next step.
    \end{enumerate}
    \item Selling a land
    \begin{enumerate}
        \item Still on the \textbf{Run} tab, expand the \textbf{sell} section for the contract instance.
        \item Provide the code output by the transaction in the previous step for the \textbf{code} parameter.
        \item Provide an address from the \textbf{Account} list which you did not use to deploy the contract or as the owner for the land for the \textbf{to} parameter.
        \item Provide any positive integer value you like for the \textbf{price} value.
        \item Click the \textbf{transact} button.
    \end{enumerate}%
\end{enumerate}%

\end{document}%